Counterfactual Training

### 2024-12-18 paper/presenations/slides.qmd
sequentially might work?

---
title: Counterfactual Training
subtitle: Update Meeting Dec 2024
author: 
  - name: "**Patrick Altmeyer**"
    url: https://www.patalt.org/
  - name: Arie van Deursen
  - name: Cynthia C. S. Liem
institute: Delft University of Technology
date: today
format: 
  tudelft-revealjs:
    theme: custom.scss
    self-contained: true
    smaller: false
    scrollable: true
    preview-links: auto
    slide-number: true
    transition: slide
    background-transition: fade
    fig-align: center
    html-math-method: mathjax
    include-in-header:
      - text: |
          <script>
          MathJax = {
            options: {
              menuOptions: {
                settings: {
                  assistiveMml: false
                }
              }
            }
          };
          </script>
revealjs-plugins:
  - pointer
crossref: 
  prp-title: RQ
  prp-prefix: RQ
classoption: "notheorems"
---

@@

$$
\ell_{\text{clf}}(f(x),y) + \lambda_{\text{adv}} \ell_{\text{clf}}(f(x^\prime),y) + \lambda_{\text{gen}} \ell_{\text{gen}}(x^\prime,x) + \text{reg}
$$

>>>>

---
title: Counterfactual Training
subtitle: Update Meeting Dec 2024
author: 
  - name: "**Patrick Altmeyer**"
    url: https://www.patalt.org/
  - name: Arie van Deursen
  - name: Cynthia C. S. Liem
institute: Delft University of Technology
date: today
format: 
  tudelft-revealjs:
    theme: custom.scss
    self-contained: true
    smaller: false
    scrollable: true
    preview-links: auto
    slide-number: true
    transition: slide
    background-transition: fade
    fig-align: center
    html-math-method: mathjax
    include-in-header:
      - text: |
          <script>
          MathJax = {
            options: {
              menuOptions: {
                settings: {
                  assistiveMml: false
                }
              }
            }
          };
          </script>
crossref: 
  prp-title: RQ
  prp-prefix: RQ
classoption: "notheorems"
---

@@

$$
\ell_{\text{clf}}(f(x),y) + \lambda_{\text{gen}} \ell_{\text{gen}}(x^\prime,x) + \lambda_{\text{adv}} \ell_{\text{clf}}(f(x^\prime),y) + \text{reg}
$$
